---
title: "Preparing NBA Stat Data"
output: html_document
date: "April 27, 2019"
author: "Max Blasdel"
---
# Purpose

Scrape website for NBA stats and convert to acceptable form for JavaScript application
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load packages
```{r message=FALSE,warning=FALSE}
library(tidyverse)
library(rvest)
library(magrittr)
```

Set base url and sub domains
```{r}
## Identify the url from where you want to extract data
base_url <-"https://www.basketball-reference.com/players/"
webpage <- read_html(base_url)
# Links to the player pages by letter
alphabet_links <- html_nodes(webpage, "#content li > a")

# convert to characters
alphabet_links <- as.character(html_text(alphabet_links))

#only take first 25 as there is no 'X'
alphabet_links<-alphabet_links[1:25] 
# establishes end of url that applies to each webpage
alphabet_links<-tolower(alphabet_links) 
```

Loop through each link and scrape data of interest from pages
```{r}
playerStats <- tibble()
for (i in 1:length(alphabet_links)) {
  BBall.url <- paste0("https://www.basketball-reference.com/players/",alphabet_links[i],"/")
  BBall.Pages<-read_html(BBall.url)
  # it is easiest to take entire table and get rid of unneeded data later on
  t <- html_node(BBall.Pages, "table") 
  t <- html_table(t)
  
  # bind together
  playerStats <- rbind(playerStats, t)
}
# drop position
playerStats %<>% select(-Pos, -Colleges)
playerStats %>% head()
```

Height is expressed with a hyphen
This needs to be converted to numeric
```{r}
playerStats %<>% 
  mutate(Ht = sapply(strsplit(as.character(playerStats$Ht),"-"), function(x) {
  12 * as.numeric(x[1]) + as.numeric(x[2])}))

# calculate career length
playerStats %<>% 
  mutate(careerLength = To - From + 1) %>%  # adding 1 to account for how seasons are recorded on the site
  select(-c(To, From))
```

Convert Birth Date to just year
```{r}
playerStats %<>% 
  mutate(birthDate = sapply(strsplit(playerStats$`Birth Date`, split = " "), function(x) {
  as.numeric(x[3])
 }))
playerStats %<>% 
  select(-`Birth Date`)
```

## Write out into a usable form for Chart.js

Base R hack for creating a js file that can be read as an array in JavaScript. This will only write the dataframe contents, no headers, so you will need to keep track of what the variables represent.
```{r}
stats<-paste("[\"",playerStats$Player,"\",\"", playerStats$Ht,"\",\"" , playerStats$Wt,"\",\"" , playerStats$careerLength,"\",\"" , playerStats$birthDate, "\"],", sep = "")
print(stats[1:6])
```

This method requires some post processing in a text editor to add the var name
Open in sublime text and add 'var stats = '
Add to html script and call as 'stats'
I wont use this method even though it is slighly more space efficient as I want to have a JSON object.
```{r eval=FALSE}
writeLines(stats, "stats.js")
```

This is another method that uses a specialized library specifically for creating and manipulating JSON files. First couple lines shown for brevity.
```{r message=FALSE, warning=FALSE}
require(jsonlite)

json_stats <- toJSON(playerStats, pretty = T)
```

Write out for use in app
```{r eval=FALSE}
write_lines(paste("var stats = ", json_stats), "nba_stats.js")
```


