---
title: "Data Analysis"
subtitle: "SERC Project"
author: "SERC Researcher"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_float: false
  #  code_folding: "hide" # only works for HTML output
    css: style.css
    self_contained: yes
    mode: selfcontained 
---
<script>
   $(document).ready(function() {
     $head = $('#header');
     $head.prepend('<img src=\"serc.png\" style=\"float: right;width: 150px;\"/>')
   });
</script>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = F)

# For R projects
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
options(stringsAsFactors = F,
        scipen = 20)
```

# Overview

What is this markdown about?

***

# Load Libraries
***
This is a good place to include any other custom functions you will be using
```{r}
library(ggplot2)
library(dplyr)
library(data.table)
```

# Load Data
***
Load all of the data that will be used in this analysis
```{r}

```

# Analysis
***
The bulk of the document
```{r}

```

# Summary Plots
***
Summarize the data with a few informative plots
```{r}

```

# Write Results
***
Only write out results at the end of the script. Hold back from writing any kind of intermediate data
```{r eval=FALSE}

```

